### 2022-11-15 dissertation/chapters/08-results.tex
🚧 (results): Save point before removing adult dataset

\noindent
All the required background information on all the elements relevant to the empirical process have been presented in Chapters~\ref{chap:anns}-\ref{chap:probability}. The proposed \acf{BHH} was presented in Chapter~\ref{chap:bhh} and the design and methodology of the empirical process was presented in Chapter~\ref{chap:methodology}. The methodology presented a number of experiments to conduct, including a case study on the behaviour of the \acs{BHH} during training, and a comparison to the performance of state-of-the-art, standalone, low-level \index{heuristic}heuristics. The methodology also defined a number of experiments related to the empirical testing of the effects of hyper-parameters on the outcomes of the \acs{BHH}.

Finally, this chapter provides the outcome of these empirical processes and provides results on all the experiments that have been conducted. Detailed discussions follow on the outcomes of each experiment. Discussions are accompanied by figures and plots to help provide visual aid for the discussions. The output of the statistical analysis that yielded the results presented in the chapter is provided in Appendix~\ref{app:statistical_analysis}. The remainder of the chapter is structured as follows.

\begin{itemize}
	\item \textbf{Section \ref{sec:results:case_study}} provides detailed discussions on the outcomes of the case study on the behaviour of the \acs{BHH}. Illustrations are provided to show the outcomes of the learning process of the \acs{BHH}, while training the underlying \acf{FFNN}.

@@

	\item \textbf{Section \ref{sec:results:overfitting}} provides a brief discussion on overfitting as it is observed for some of the empirical tests.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% METRICS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PARAMS ALPHAS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[0].pdf}
	\caption{The average value of the concentration parameter $\alpha_{0}$ (\acs{SGD}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:alpha:0}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[6].pdf}
	\caption{The average value of the concentration parameter $\alpha_{6}$ (\acs{Adam}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:alpha:6}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[7].pdf}
	\caption{The average value of the concentration parameter $\alpha_{7}$ (\acs{PSO}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:alpha:7}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[8].pdf}
	\caption{The average value of the concentration parameter $\alpha_{8}$ (\acs{GA}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:alpha:8}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PARAMS THETAS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[0].pdf}
	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{0}$ (\acs{SGD}), given concentration parameter $\alpha_{0}$, sampled from the probability distribution $P(\theta_{0} \vert \alpha_{0})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:theta:0}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[6].pdf}
	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{6}$ (\acs{Adam}), given concentration parameter $\alpha_{6}$, sampled from the probability distribution $P(\theta_{6} \vert \alpha_{6})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:theta:6}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[7].pdf}
	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{7}$ (\acs{PSO}), given concentration parameter $\alpha_{7}$, sampled from the probability distribution $P(\theta_{7} \vert \alpha_{7})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:theta:7}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[8].pdf}
	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{8}$ (\acs{GA}), given concentration parameter $\alpha_{8}$, sampled from the probability distribution $P(\theta_{8} \vert \alpha_{8})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:theta:8}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PARAMS P_H (Priors)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[0].pdf}
	\caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the probability of the selection probability, denoted by $\theta_{0}$, sampled from the prior selection probability distribution $P(h_{0} \vert \theta_{0})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_H:0}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[6].pdf}
	\caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the probability of the selection probability, denoted by $\theta_{6}$, sampled from the prior selection probability distribution $P(h_{6} \vert \theta_{6})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_H:6}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[7].pdf}
	\caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the probability of the selection probability, denoted by $\theta_{7}$, sampled from the prior selection probability distribution $P(h_{7} \vert \theta_{7})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_H:7}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[8].pdf}
	\caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the probability of the selection probability, denoted by $\theta_{8}$, sampled from the prior selection probability distribution $P(h_{8} \vert \theta_{8})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_H:8}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PARAMS P_HgEC (Posterior)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][0].pdf}
	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{0} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_HgEC:0:0}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][6].pdf}
	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{6} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_HgEC:0:6}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][7].pdf}
	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{7} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_HgEC:0:7}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][8].pdf}
	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{8} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_HgEC:0:8}
\end{figure}

\section{BHH vs. Low-Level Heuristics}\label{sec:results:standalone}

>>>>

The required background information on all the elements relevant to the empirical process have been presented in Chapters~\ref{chap:anns}-\ref{chap:probability}. The proposed \acf{BHH} was presented in Chapter~\ref{chap:bhh} and the design and methodology of the empirical process was presented in Chapter~\ref{chap:methodology}. The methodology presented a number of experimental groups to conduct, including a case study on the behaviour of the \acs{BHH} during training, and a comparison to the performance of state-of-the-art, standalone, low-level \index{heuristic}heuristics. The methodology also defined a number of experiments related to the empirical testing of the effects of hyper-parameters on the outcomes of the \acs{BHH}.

Finally, this chapter provides the outcome of these empirical processes and provides results on all the experiments that have been conducted. Detailed discussions follow on the outcomes of each experiment. Discussions are accompanied by figures and plots to help provide visual aid for the discussions. The output of the statistical analysis that yielded the results that is presented in the chapter is provided in Appendix~\ref{app:statistical_analysis}. The remainder of the chapter is structured as follows.

\begin{itemize}
	\item \textbf{Section \ref{sec:results:case_study}} provides detailed discussions on the outcomes of the case study on the behaviour of the \acs{BHH}. Illustrations are provided to show the change in parameter values to illustrate the outcomes of the learning process of the \acs{BHH}, while training the underlying \acf{FFNN}.

@@

@@

This section provides the empirical results of the case study on the behaviour of the \acs{BHH} as it is used to train a \acs{FFNN} on the iris dataset. As a reminder, the iris dataset contains 150 records, split into a training dataset containing 120 records, and a test dataset that contains 30 records. The test dataset is treated like a validation dataset, and is evaluated at every training step to illustrate the outcomes of the \acs{BHH} throughout the training process. Some noisiness can be expected as mini-batch training is executed with batch sizes of 30. The results that are presented are averaged over 30 independent runs.

Furthermore, the case study focuses on three different variants of the \acs{BHH}. These include the baseline configuration as was provided in Chapter~\ref{chap:bhh}, as well as a configuration that includes a ``long memory'' by setting the replay window size to 250, and a configuration that makes use of the \textit{symmetric} credit assignment strategy. These configurations were specifically chosen for the following reasons: the large replay window size configuration is chosen to illustrate a case where the \acs{BHH} does not ``forget'' past performances of the low-level \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and the configuration that utilises the symmetric credit assignment is chosen to illustrate a case where there \acs{BHH} does not reward good performance and does not yield a bias towards \index{heuristic}heuristics that perform well. This section is structured as follows.

\begin{itemize}
	\item \textbf{Section \ref{sec:results:case_study:performance_metrics}} provides illustrations and discussions around the outcomes of the performance metrics as obtained by the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:case_study:concentration_parameters}} provides illustrations and discussions around the changes in concentration parameter values as a result of the learning process implemented by the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:case_study:probs_of_select_probs}} provides illustrations and discussions around the changes in the \textit{probabilities of \index{heuristic}heuristic selection probabilities} as a result of the learning process implemented by the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:case_study:prior_selec_prob}} provides illustrations and discussions around the changes in the \textit{prior \index{heuristic}heuristic selection probabilities} as a result of the learning process implemented by the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:case_study:posterior_selec_prob}} provides illustrations and discussions around the changes in the \textit{posterior \index{heuristic}heuristic selection probabilities} as a result of the learning process implemented by the \acs{BHH}.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% METRICS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Performance metrics}\label{sec:results:case_study:performance_metrics}

Figures~\ref{fig:results:case_study:train_loss}-\ref{fig:results:case_study:test_accuracy} provide illustrations of the train and test, loss and accuracy plots over 30 epochs and is illustrated in log scale. The first logical observation that can be made is that the \acs{BHH} was indeed able to successfully train the underlying \acs{FFNN}. The noisiness that results from mini-batch training can be observed in Figure~\ref{fig:results:case_study:test_loss}. Figures~\ref{fig:results:case_study:train_accuracy} and~\ref{fig:results:case_study:test_accuracy} show that the trained \acs{FFNN} achieved an accuracy of almost 100\%. Although the \acs{BHH} was able to succesfully train the underlying \acs{FFNN}, in this particular case, there is no clear distinction between the performance of any of the configurations under consideration. However, it should be noted from epochs 5 and onwards presented in Figure~\ref{fig:results:case_study:test_accuracy} that all the configurations of the \acs{BHH} was able to ``undo'' selections that yielded worse test loss results in the previous epoch. The sporadic, oscillating nature of the results later in the training process is simply a result of momentum that is maintained between low-level \index{heuristic}heuristics. For example, momentum can be built up by one of the gradient-based heuristics, after which the \acs{BHH} switches to another heuristic in an attempt to find better solutions. The \acs{BHH} does not incorporate a \textit{move acceptance} strategy, whereby a heuristic's outcome is rejected if it does not improve on previous results, yielding a possibly worse loss measurement. A move acceptance strategy can be utilised on a validation set as a mechanism to approve or reject heuristic progressions from one step to the other.

Finally, it should be noted that the \acs{BHH} implements learning at every mini-batch step, while Figures~\ref{fig:results:case_study:train_loss}-\ref{fig:results:case_study:test_accuracy} only provide the outcomes of performance metrics at the end of each epoch. Further investigation is required at a mini-batch step level.

@@

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % PARAMS ALPHAS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Concentration Parameters}\label{sec:results:case_study:concentration_parameters}

To illustrate the learning process undergone by the \acs{BHH}, further investigation is required. Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the \index{Dirichelet probability distribution}Dirichelet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, from which prior \textit{probabilities of selection probabilities} are sampled. Figures~\ref{fig:results:case_study:alpha:0}-\ref{fig:results:case_study:alpha:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, 8 respectively. Index 0, 6, 7, 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively and only represent a subset of the concentration parameters in $\boldsymbol{\alpha}$ and the \index{heuristic pool}heuristic pool. Simular illustrations for the other indices in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[0].pdf}
	\caption{The average value of the concentration parameter $\alpha_{0}$ (\acs{SGD}) over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:alpha:0}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[6].pdf}
	\caption{The average value of the concentration parameter $\alpha_{6}$ (\acs{Adam}) over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:alpha:6}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[7].pdf}
	\caption{The average value of the concentration parameter $\alpha_{7}$ (\acs{PSO}) over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:alpha:7}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[8].pdf}
	\caption{The average value of the concentration parameter $\alpha_{8}$ (\acs{GA}) over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:alpha:8}
\end{figure}

The first logical observation to be made from Figures~\ref{fig:results:case_study:alpha:0}-\ref{fig:results:case_study:alpha:8} is the step-wise increasing nature of $\boldsymbol{\alpha}$ for the long memory configuration (denoted \textit{bhh\_replay\_250}), illustrated in green. Since the replay window size is sufficienty large to contain the performance log for all the steps executed in the training process, the \acs{BHH} does not forget past performances of low-level heuristics. The values in $\boldsymbol{\alpha}$ is never reset to its initial value of 1, and thus $\boldsymbol{\alpha}$ continues to increase throughout the training process. However, it should be noted that the rate and degree of change is different for different indices of $\boldsymbol{\alpha}$. The aforementioned observation is the first indicator of the learning process yielded by the \acs{BHH}. Heuristics that perform will will see their corresponding element in $\boldsymbol{\alpha}$ increase more rapidly that other heuristics that do not perform well.

The next observation that can be made is for the baseline configuration (denoted \textit{bhh\_baseline}) in red, and the symmetric credit assignment strategy configuration (denoted \textit{bhh\_credit\_symmetric}) in blue. Both these configurations see $\boldsymbol{\alpha}$ being reset to its initial value of 1 as regular intervals. This interval is represented by the \textit{reanalysis} window size. The reanalysis interval dictates the frequency at which Bayesian analysis is conducated on the performance log, mainted by the \acs{BHH}. Bayesian analysis is used to update $\boldsymbol{\alpha}$. As a result, small plateaus appear where $\boldsymbol{\alpha}$ does not change. Notice that $\boldsymbol{\alpha} \geq 1$ for multiple indices, even after reanalysis. This is because the same heuristic can be allocated to multiple entities, each contributing a minimum pseudo-count gain of 1 at the corresponding index in $\boldsymbol{\alpha}$ through the Bayesian analysis process. In a case where all 5 entities in the entity pool are allocated the same heuristic, for all 10 steps in the reanalysis windown, $\boldsymbol{\alpha} = 50$.

Furthermore, it is important to mention that a change in $\boldsymbol{\alpha}$ between reanalysis windows does not yet necessarily indicate that the \acs{BHH} is learning. The concentration parameter $\boldsymbol{\alpha}$ tracks the \textit{occurance} of the random event of observing heuristics (denoted $\boldsymbol{{H}}$). \index{heuristic}Heuristics can be observed as a result of good performance, by which the \acs{BHH} then learns to frequenctly reselect these \index{heuristic}heuristics again, or just by chance through the probabilistic sampling nature of the \acs{BHH}. Further investigation is required to illustrate the learning mechanism of the \acs{BHH}.

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % PARAMS THETAS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Probabilities of Selection Probabilities}\label{sec:results:case_study:probs_of_select_probs}

This section provides a detailed investigation into the \textit{probabilities of selection probabilities}, denoted by $\boldsymbol{\theta}$, as it changes throughout the training process. As a reminder, the \acs{BHH} implements a Bayesian view of probabilistic modeling and thus, \index{heuristic}heuristic selection probabilities are defined by an underlying probablistic distribution themselves. The probability distribution of \index{heuristic}heuristic selection probabilities is denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ and the prior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.

Figures~\ref{fig:results:case_study:theta:0}-\ref{fig:results:case_study:theta:8} provide illustrations of the probabilities of the selection probabilities, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs. These illustrations are presented in log scale. Similar to what is previously mentioned, \textit{probabilities of selection probabilities} at index 0, 6, 7, 8 represent the probabilities of selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively and only represent a subset of the probabilities of selection probabilities in $\boldsymbol{\theta}$ and the \index{heuristic pool}heuristic pool. Once again, simular illustrations for the other indices in $\boldsymbol{\theta}$ are left out for brevity as they contain similar illustrations.

From the illustrations presented in Figures~\ref{fig:results:case_study:theta:0}-\ref{fig:results:case_study:theta:8}, a clearer picture off the learning process of the \acs{BHH} is formed. The first important observation to make is for the bhh\_replay\_250 configuration, presented in green. As a reminder, 10 low-level \index{heuristic}heuristics are included in the heuristic pool, yielding a probability of selection probability of 0.1 for each \index{heuristic}heuristic by the frequentist view of probabilistic modeling. Towards the end of the training process, the probability of selection probability converges back to the symmetrical, uniform probability distribution, yielding a probability of selection probability of 0.1 per \index{heuristic}heuristic. This can be explained as follows: most of the training progress is made in the early stages of the training process, and training stagnates towards the end of the training process. Since training stagnates, all heuristics, no matter their past performances, struggle to yield better solutions towards the end of the training process. As a result of stagnation, heuristics then struggle to yield credit allocations by means of the credit assignment strategy. In the case study experimental group, both the bhh\_baseline and bhh\_replay\_250 configurations make use of the \textit{ibest} credit assignment strategy. The \textit{ibest} credit assignment strategy allocates credit to the heuristic that provided the best performance for the current iteration/step and thus, towards the end of the training process, any random heuristic can yield the best iteration performance. However, since the bhh\_baseline has a short reanalysis interval, the concentration parameter $\boldsymbol{\alpha}$ gets reset to its default value of 1 more often than the bhh\_replay\_250 configuration, resulting in a probability distribution that is less narrow and thus explaining the larger variance of $\boldsymbol{\theta}$ throughout.

Another observation to make occurs in the first 30 steps of the training process. Notice how all three configurations mostly yield the same probabilities of selection probabilities in these first 30 steps. This can be explained as follows: all three configurations use a different random seed per run, but use the same random seed across configurations for the same runs. This is done so that any difference in the behaviour of the different \acs{BHH} configurations are then not a result of random sampling, but solely because of differences in their approaches. This is especially applicable to the initialisation process, where entities are randomly placed in the search space, as well as the early stages of training, where most of the training progress is made. It should be noted that, despite using the same random seed across configurations for the same runs, after about 30 steps, the behavioural changes between the configurations start the show. As a reminder, the bhh\_credit\_symmetric configuration, does not bias towards best performing \index{heuristic}heuristics and thus, where the bhh\_baseline and bhh\_replay\_250 configurations diverge from the behaviour of the bhh\_credit\_symmetric configuration, the difference in behaviour is proof of the effect of performance bias.

Finally, despite divergence in behaviour, the bhh\_baseline configuration and the bhh\_credit\_symmetric configuration both yield similar sporadic behaviour, much more so than with the bhh\_replay\_250 configuration. This can be attributed to a very small reanalysis window that contains very few samples to learn from (N=10). A small reanalysis window allows for more exploration, but can also yield greater variance of the probabilities of selection probabilities. Once again, any differences then in the behaviour of the  bhh\_baseline compared to the bhh\_credit\_symmetric configurations is proof of small performance exploitations.

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[0].pdf}
	\caption{The average sampled probability of the selection probability, denoted $\theta_{0}$ (\acs{SGD}), given concentration parameter $\alpha_{0}$. The probability of the selection probability is sampled from the probability distribution, denoted $P(\theta_{0} \vert \alpha_{0})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:theta:0}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[6].pdf}
	\caption{The average sampled probability of the selection probability, denoted $\theta_{6}$ (\acs{Adam}), given concentration parameter $\alpha_{6}$. The probability of the selection probability is sampled from the probability distribution, denoted $P(\theta_{6} \vert \alpha_{6})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:theta:6}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[7].pdf}
	\caption{The average sampled probability of the selection probability, denoted $\theta_{7}$ (\acs{PSO}), given concentration parameter $\alpha_{7}$. The probability of the selection probability is sampled from the probability distribution, denoted $P(\theta_{7} \vert \alpha_{7})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:theta:7}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[8].pdf}
	\caption{The average sampled probability of the selection probability, denoted $\theta_{8}$ (\acs{GA}), given concentration parameter $\alpha_{8}$. The probability of the selection probability is sampled from the probability distribution, denoted $P(\theta_{8} \vert \alpha_{8})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:theta:8}
\end{figure}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % PARAMS P_H (Priors)
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Prior Selection Probabilities}\label{sec:results:case_study:prior_selec_prob}

This section provides a brief investigation into the \textit{prior \index{heuristic}heuristic selection probabilities}, that results from the probabilistic model implemented by the \acs{BHH}. The prior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.

Figures~\ref{fig:results:case_study:p_H:0}-\ref{fig:results:case_study:p_H:8} provide illustrations of the prior\index{heuristic}heuristic selection probabilities, sampled from the \index{heuristic}heuristic selection probability distribution $P(\boldsymbol{H} \vert \boldsymbol{\theta})$ throughout the training process, and averaged over all 30 runs. Similar to before, these illustrations are also presented in log scale. The main observation to make from these figures is that they are much less sporadic than the figures presented for the probabilities of selection probabilities. This is because of the \textit{reselection} interval hyper-parameter. A reselection interval hyper-parameter is introduces to control the frequency by which new heuristics are allocated to each entity. Since the default \textit{reselection} interval is set to 10, the \index{heuristic}heuristic selection probabilities are only resampled at intervals of 10. These illustrations then simply yield rough approximations of the illustrations provided in Figures~\ref{fig:results:case_study:theta:0}-\ref{fig:results:case_study:theta:8} for the probabilities of selection probabilities. As such, the same observations and conclusions that are made in Section \ref{sec:results:case_study:probs_of_select_probs} also apply in this section.

Finally, it should be mentioned that at each step, the goal of the \acs{BHH} is to update these prior ``beliefs'' based on newly observed evidence of \index{heuristic}heuristic performances. Since these prior \index{heuristic}heuristic selection probabilities change over time, it can be concludes that the change in prior \index{heuristic}heuristic selection probabilities is a result of the learning mechanism of the \acs{BHH}. Furthermore, these prior \index{heuristic}heuristic selection probability distributions provide an opportunity to utilise prior knowledge by some expert to inject heuristic selection biases, even before training starts.

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[0].pdf}
	\caption{The average sampled prior \index{heuristic}heuristic selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the probability of the selection probability, denoted by $\theta_{0}$. The prior \index{heuristic}heuristic selection probability is sampled from the prior \index{heuristic}heuristic selection probability distribution, denoted $P(h_{0} \vert \theta_{0})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_H:0}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[6].pdf}
	\caption{The average sampled prior \index{heuristic}heuristic selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the probability of the selection probability, denoted by $\theta_{6}$. The prior \index{heuristic}heuristic selection probability is sampled from the prior \index{heuristic}heuristic selection probability distribution, denoted $P(h_{6} \vert \theta_{6})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_H:6}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[7].pdf}
	\caption{The average sampled prior \index{heuristic}heuristic selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the probability of the selection probability, denoted by $\theta_{7}$. The prior \index{heuristic}heuristic selection probability is sampled from the prior \index{heuristic}heuristic selection probability distribution, denoted $P(h_{7} \vert \theta_{7})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_H:7}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[8].pdf}
	\caption{The average sampled prior \index{heuristic}heuristic selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the probability of the selection probability, denoted by $\theta_{8}$. The prior \index{heuristic}heuristic selection probability is sampled from the prior \index{heuristic}heuristic selection probability distribution, denoted $P(h_{8} \vert \theta_{8})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_H:8}
\end{figure}
